Investigating Biases Associated with Dietary Starch Incorporation and Retention with an Oral Biofilm Model

### 2022-06-08 analysis/paper/paper.Rmd
update references

plt2_ph1 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate2_photometric1.csv"),
  col_names = F)
plt2_ph2 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate2_photometric2.csv"),
  col_names = F)
# starch counts in samples
raw_counts <- readr::read_csv(here("analysis/data/raw_data/starch_counts.csv"))
# starch counts in solutions
sol_counts <- readr::read_csv(here("analysis/data/raw_data/solution_counts.csv"))
# load R scripts
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
source(here("analysis/scripts/amylase-assay.R"))
readr::write_csv(sol_corr, here("analysis/data/derived_data/sol_corr.csv"))
readr::write_csv(corr_counts, here("analysis/data/derived_data/corr_counts.csv"))
readr::write_csv(corr_comb, here("analysis/data/derived_data/corr_comb.csv"))
## Compile refs.bib using rbbt package ##
cite_keys <- rbbt::bbt_detect_citations(list.files(pattern = ".Rmd"))
#cite_keys <- unlist(cite_keys, use.names = FALSE)
try(
  rbbt::bbt_write_bib(here("analysis/paper/refs.bib"), keys = cite_keys, overwrite = T, translator = "bibtex")
  #rbbt::bbt_update_bib(here("analysis/paper/paper.Rmd"), here("analysis/paper/refs.bib"))
)
# ## end refs.bib ##
# 
# ## Word count ##
# wd_count <- wordcountaddin::word_count()
cor_r <- signif(count_cor$estimate, 3)
cor_ci <- signif(count_cor$conf.int, 3)
cor2_r <- signif(count_cor$estimate, 3)
cor2_ci <- signif(count_cor$conf.int, 3)
```

>>>>

plt2_ph1 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate2_photometric1.csv"),
  col_names = F)
plt2_ph2 <- readr::read_tsv(
  here("analysis/data/raw_data/ExpM_plate2_photometric2.csv"),
  col_names = F)
# starch counts in samples
raw_counts <- readr::read_csv(here("analysis/data/raw_data/starch_counts.csv"))
# starch counts in solutions
sol_counts <- readr::read_csv(here("analysis/data/raw_data/solution_counts.csv"))
# load R scripts
source(here("analysis/scripts/analysis.R"))
source(here("analysis/scripts/tables.R"))
source(here("analysis/scripts/figures.R"))
source(here("analysis/scripts/amylase-assay.R"))
readr::write_csv(sol_corr, here("analysis/data/derived_data/sol_corr.csv"))
readr::write_csv(corr_counts, here("analysis/data/derived_data/corr_counts.csv"))
readr::write_csv(corr_comb, here("analysis/data/derived_data/corr_comb.csv"))
## Compile refs.bib using rbbt package ##
cite_keys <- rbbt::bbt_detect_citations(list.files(pattern = ".Rmd"))
#cite_keys <- unlist(cite_keys, use.names = FALSE)
try(
  #rbbt::bbt_write_bib(here("analysis/paper/refs.bib"), keys = cite_keys, overwrite = T, translator = "bibtex")
  rbbt::bbt_update_bib(here("analysis/paper/paper.Rmd"), here("analysis/paper/refs.bib"))
)
# ## end refs.bib ##
# 
# ## Word count ##
# wd_count <- wordcountaddin::word_count()
cor_r <- signif(count_cor$estimate, 3)
cor_ci <- signif(count_cor$conf.int, 3)
cor2_r <- signif(count_cor$estimate, 3)
cor2_ci <- signif(count_cor$conf.int, 3)
```
